%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% chap: Conclusion %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Conclusions \& Future work }\label{chapter:chap6}

\section{Conclusion}\label{sect:Conclusion}

In conclusion, the development of such applications represents an important step in the everyday user's ability to control and maintain their phones' storage and in keeping the phone clean of any unwanted data. Without such applications, most of us would be unaware of the reasons why our phones' storage capacity is being drained without our input. As such, the disadvantage of not being able to use our memory space however we want is diminished, leaving us with more freedom for how we use our phones.

This process of data cleaning can have lasting effects on the phone's life, most people not being aware of the fact that they can improve the lifespan of their phone by such methods. Too often one hears that people need to change their phone because it started to work slower, or that they need to buy one because they have too little memory left in it. With this in mind, making sure that our phone is well kept and once in a while cleaned is the same as cleaning our own homes, no one wants to live in a filthy house, so our phones should be treated with the same manner of respect.

\section{Future work}\label{sect:Future work}

Further improvements to applications such as this one are possible, ranging from data analysis over a set period of time to media optimization, such as the removal of duplicate image, audio, or video files, the management of notifications, application analysis, and so on.

Other areas that can be looked on are:

- Automation: We could look to improve the automation of data cleaning processes. This involves the development of new algorithms and techniques for automatically detecting errors in data. With the current \ac{AI} revolution, such automation processes could be the future of data-cleaning applications;

- The handling of complex data types: With data becoming more complex each passing day, there might come a growing need for data cleaning methods that can handle these types of complex data types and structures. 